---
title: "Beer Usage Forecasting Repotr"
subtitle: "BI Report for Beer Industry Operations"
author: "Gerry"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    code_folding: hide
    df_print: paged
  pdf_document:
    toc: true
    number_sections: true
params:
  forecast_horizon: 3
  confidence_level: 0.95
  alert_threshold: 0.20
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  warning = FALSE, 
  message = FALSE,
  fig.width = 12,
  fig.height = 8,
  dpi = 300
)

# Required libraries
library(prophet)
library(dplyr)
library(ggplot2)
library(knitr)
library(kableExtra)
library(plotly)
library(DT)
library(formattable)
library(scales)

# Set theme for consistent plotting
theme_set(theme_minimal())
```

# 🚨 EXECUTIVE BRIEF: Critical Supply Chain Disruption Risk

## PROBLEM: Imminent Material Shortage Crisis

### Financial Impact Assessment
- **Potential Revenue Loss**: $3.2M over next 90 days
- **Emergency Procurement Premium**: +$520K (40% above standard rates)
- **Customer Contract Penalties**: $240K for delivery delays
- **Market Share Risk**: 15% of premium segment vulnerable to competitors

### Severity Dashboard
```{r executive-problem-metrics, echo=FALSE}
critical_metrics <- data.frame(
  Product_Line = c("Craft IPA Premium", "Seasonal Holiday", "Light Lager Core", "Specialty Stouts"),
  Days_Remaining = c("6 days", "4 days", "11 days", "8 days"),
  Standard_Lead_Time = c("21 days", "28 days", "18 days", "25 days"),
  Risk_Level = c("CRITICAL", "CRITICAL", "HIGH", "CRITICAL"),
  Revenue_Exposure = c("$1.1M", "$890K", "$750K", "$630K")
)

critical_metrics %>%
  kable(caption = "Material Shortage Risk Assessment - Immediate Action Required") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(4, color = "white", 
              background = ifelse(critical_metrics$Risk_Level == "CRITICAL", "#dc3545", "#fd7e14")) %>%
  column_spec(5, bold = TRUE, color = "#dc3545")
```

**Why Act Within 24 Hours:**
- Primary suppliers experiencing force majeure delays (3-4 weeks)
- Competitor stockpiling detected in market intelligence
- Q2 peak demand surge begins in 8 days
- Insurance coverage excludes supply chain disruption losses

---

## SOLUTIONS: Three Immediate Response Options

### Option 1: Full Emergency Procurement Protocol
**Timeline**: 48-72 hours | **Investment**: $520K | **Success Rate**: 95%

- Activate all pre-approved secondary suppliers immediately
- Charter expedited freight for critical materials
- Establish 60-day inventory buffer across all product lines
- **Expected Outcome**: Zero production interruption, full capacity maintained

### Option 2: Strategic Production Pivot
**Timeline**: 24 hours | **Investment**: $75K | **Success Rate**: 70%

- Shift production to high-margin, low-material products (30 days)
- Prioritize tier-1 customer commitments only
- Negotiate controlled delivery delays with tier-2/3 accounts
- **Expected Outcome**: $2.1M revenue protected, controlled customer impact

### Option 3: Hybrid Crisis Management (RECOMMENDED)
**Timeline**: 36 hours | **Investment**: $315K | **Success Rate**: 92%

- Emergency procurement for critical/high-risk materials only
- Production optimization for standard products
- Premium freight for highest-value customer orders
- **Expected Outcome**: 96% revenue preservation, minimal market disruption

```{r solution-matrix, echo=FALSE}
solution_comparison <- data.frame(
  Strategy = c("Full Emergency", "Production Pivot", "Hybrid Management"),
  Investment = c("$520K", "$75K", "$315K"),
  Timeline = c("72 hours", "24 hours", "36 hours"),
  Revenue_Protected = c("100%", "65%", "96%"),
  Customer_Impact = c("None", "Moderate", "Minimal"),
  Risk_Mitigation = c("Complete", "Partial", "Comprehensive")
)

solution_comparison %>%
  kable(caption = "Crisis Response Strategy Comparison") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  row_spec(3, bold = TRUE, color = "white", background = "#28a745")
```

---

## ASK: Immediate Executive Authorization

### Budget Authorization Required
- **Amount**: $315,000 (Hybrid Crisis Management)
- **Funding Source**: Emergency Operations Reserve
- **ROI Projection**: 10.2:1 (Revenue protected vs. investment)
- **Payback Period**: 45 days

### Resource Deployment
```{r resource-requirements, echo=FALSE}
resource_table <- data.frame(
  Role = c("Executive Sponsor", "Emergency Procurement", "Operations Coordination", "Finance Authorization", "Logistics Management"),
  Personnel = c("VP Operations", "2 Senior Buyers", "1 Production Manager", "CFO Approval", "1 Supply Chain Lead"),
  Time_Commitment = c("Oversight", "72 hours full-time", "48 hours full-time", "2 hours", "60 hours"),
  Availability = c("Confirmed", "Ready", "Ready", "Pending", "Ready")
)

resource_table %>%
  kable(caption = "Required Resource Deployment") %>%
  kable_styling(bootstrap_options = c("striped", "condensed")) %>%
  column_spec(4, color = "white",
              background = ifelse(resource_table$Availability == "Pending", "#dc3545", "#28a745"))
```

### Decision Timeline - CRITICAL PATH
1. **Executive Decision**: Required by 5:00 PM TODAY
2. **Budget Approval**: 9:00 AM tomorrow (CFO)
3. **Supplier Activation**: 2:00 PM tomorrow
4. **First Emergency Deliveries**: Day 3
5. **Crisis Resolution**: Day 5

**IMMEDIATE CONTACT**: Sarah Martinez, VP Operations | sarah.martinez@company.com | (555) 234-5678

---

# Executive Summary {.tabset}

## Overview

This report provides comprehensive material usage forecasting for beer industry operations, delivering actionable insights for strategic planning, procurement, and operational optimization.

**Key Highlights:** - Forecasting horizon: `r params$forecast_horizon` months - Confidence level: `r params$confidence_level * 100`% - Alert threshold: `r params$alert_threshold * 100`%

## Business Impact

```{r business-metrics, echo=FALSE}
# Business impact metrics (example data - replace with actual calculations)
impact_metrics <- data.frame(
  Metric = c("Annual Cost Savings", "Forecast Accuracy", "Stockout Reduction", 
             "Emergency Order Reduction", "Working Capital Optimization"),
  Before = c("$45M", "85%", "8%", "15%", "$12M"),
  After = c("$41.6M", "94%", "2%", "3%", "$9.8M"),
  Improvement = c("$3.4M", "+9pp", "-6pp", "-12pp", "$2.2M"),
  Impact = c("7.6%", "10.6%", "75%", "80%", "18.3%")
)

impact_metrics %>%
  kable(caption = "Business Impact Summary") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(4, color = "white", background = "#28a745") %>%
  column_spec(5, color = "white", background = "#17a2b8")
```



```{r data-setup, include=FALSE}
## Data Preparation & Model Setup ----
# Data preparation (replace with your actual data loading)
# This is a template - adjust based on your data structure

# Example data structure - replace with actual data loading
set.seed(123)
dates <- seq(as.Date("2020-01-01"), as.Date("2024-12-01"), by = "month")

# Create example key data
key <- data.frame(
  type = paste0("Type_", 1:12),
  name = c("Craft_IPA", "Light_Lager", "Wheat_Beer", "Stout_Porter", 
           "Seasonal_Ale", "Premium_Pilsner", "Fruit_Beer", "Sour_Ale",
           "Belgian_Style", "German_Lager", "American_Pale", "Holiday_Special")
)

# Create example model data
model_data <- expand.grid(
  ds = dates,
  type = key$type
) %>%
  mutate(
    # Simulate realistic beer material usage patterns
    trend = as.numeric(ds - min(ds)) * 0.02,
    seasonal = sin(2 * pi * as.numeric(format(ds, "%j")) / 365) * 20,
    noise = rnorm(n(), 0, 10),
    base_usage = case_when(
      type %in% c("Type_1", "Type_5") ~ 150,  # High usage types
      type %in% c("Type_2", "Type_6") ~ 100,  # Medium usage
      TRUE ~ 75                               # Lower usage
    ),
    month_current = pmax(0, base_usage + trend + seasonal + noise)
  ) %>%
  select(ds, type, month_current) %>%
  arrange(type, ds)

# Display data structure
cat("Data Structure Overview:\n")
cat("Date range:", min(model_data$ds), "to", max(model_data$ds), "\n")
cat("Number of product types:", length(unique(model_data$type)), "\n")
cat("Total observations:", nrow(model_data), "\n")
```


```{r prophet-modeling, include=FALSE}
## Prophet Forecasting Models ----
# Initialize results storage
model_results <- data.frame()
model_registry <- list()

# Enhanced Prophet modeling loop with progress tracking
cat("Fitting Prophet models for", nrow(key), "product types...\n")

for (i in 1:nrow(key)) {
  
  cat("Processing:", key$name[i], "- Type:", key$type[i], "\n")
  
  # Filter and prepare data for current type
  current_data <- model_data %>%
    filter(type == key$type[i]) %>%
    select(ds, y = month_current) %>%
    arrange(ds) %>%
    filter(!is.na(ds), !is.na(y))
  
  # Check for sufficient data
  if (nrow(current_data) < 10) {
    cat("Warning: Insufficient data for", key$name[i], "- skipping\n")
    next
  }
  
  tryCatch({
    # Fit Prophet model with business-relevant parameters
    model <- prophet(current_data,
                    yearly.seasonality = TRUE,
                    weekly.seasonality = FALSE,
                    daily.seasonality = FALSE,
                    changepoint.prior.scale = 0.05,
                    seasonality.prior.scale = 10)
    
    # Store model
    model_name <- paste(key$name[i], "model", sep = "_")
    model_registry[[model_name]] <- model
    
    # Generate future dataframe
    future <- make_future_dataframe(model, periods = params$forecast_horizon)
    
    # Make predictions
    predictions <- predict(model, future) %>%
      select(ds, yhat_lower, yhat_upper, yhat) %>%
      mutate(
        type = key$type[i],
        model_name = key$name[i],
        ds = as.Date(ds)
      )
    
    # Join with historical data
    results <- predictions %>%
      left_join(
        current_data %>% mutate(type = key$type[i]),
        by = c("ds", "type")
      ) %>%
      mutate(
        is_forecast = is.na(y),
        forecast_date = Sys.Date()
      ) %>%
      rename(month_current = y)
    
    # Combine results
    model_results <- rbind(model_results, results)
    
  }, error = function(e) {
    cat("Error processing", key$name[i], ":", e$message, "\n")
  })
}

cat("Model fitting complete. Total models:", length(unique(model_results$model_name)), "\n")
```

# Forecast Visualization

## Forecast Dashboard

```{r main-forecast-plot, fig.height=12}
# Create comprehensive forecast visualization
main_plot <- model_results %>%
  ggplot(aes(x = ds)) +
  geom_line(aes(y = month_current), color = "black", size = 1, na.rm = TRUE) +
  geom_line(aes(y = yhat, color = model_name), size = 1, alpha = 0.8) +
  geom_ribbon(aes(ymin = yhat_lower, ymax = yhat_upper, fill = model_name), 
              alpha = 0.2, color = NA) +
  geom_vline(
    data = model_results %>% 
      group_by(type) %>% 
      summarise(last_actual = max(ds[!is_forecast], na.rm = TRUE), .groups = "drop"),
    aes(xintercept = last_actual),
    linetype = "dashed", alpha = 0.6, color = "red"
  ) +
  facet_wrap(~model_name, scales = "free_y", ncol = 3) +
  scale_x_date(date_labels = "%Y-%m", date_breaks = "12 months") +
  scale_y_continuous(labels = comma_format()) +
  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, hjust = 1),
    strip.text = element_text(face = "bold", size = 10),
    plot.title = element_text(size = 16, face = "bold"),
    plot.subtitle = element_text(size = 12)
  ) +
  labs(
    title = "Material Usage Forecasting - Next 3 Months",
    subtitle = paste("Prophet Model Predictions with", params$confidence_level * 100, "% Confidence Intervals"),
    x = "Date",
    y = "Monthly Material Usage (Units)",
    caption = paste("Generated on:", Sys.Date(), "| Red dashed line indicates forecast start")
  )

print(main_plot)
```

## Interactive Forecast Explorer

```{r interactive-plot, fig.width=10,fig.height=2}
# Create interactive version for detailed exploration
interactive_plot <- model_results %>%
  filter(model_name %in% head(unique(model_results$model_name), 6)) %>%  # Show top 6 for performance
  plot_ly(x = ~ds, color = ~model_name) %>%
  add_lines(y = ~month_current, name = "Actual", 
            line = list(color = "black", width = 3),
            hovertemplate = "Date: %{x}<br>Actual: %{y}<extra></extra>") %>%
  add_lines(y = ~yhat, name = "Forecast",
            hovertemplate = "Date: %{x}<br>Forecast: %{y}<extra></extra>") %>%
  add_ribbons(ymin = ~yhat_lower, ymax = ~yhat_upper, 
              name = "Confidence Interval",
              hovertemplate = "Date: %{x}<br>Range: %{ymin} - %{ymax}<extra></extra>") %>%
  layout(
    title = "Interactive Material Usage Forecast",
    xaxis = list(title = "Date"),
    yaxis = list(title = "Monthly Usage"),
    hovermode = "x unified"
  )

interactive_plot
```

# Business Intelligence Reports {.tabset}

## Executive Summary

```{r executive-summary}
# Generate executive forecast summary
forecast_summary <- model_results %>%
  filter(is_forecast) %>%
  group_by(type, model_name) %>%
  summarise(
    next_month = round(first(yhat), 0),
    next_month_lower = round(first(yhat_lower), 0),
    next_month_upper = round(first(yhat_upper), 0),
    three_month_total = round(sum(yhat), 0),
    three_month_range = paste0(
      format(round(sum(yhat_lower)), big.mark = ","), " - ", 
      format(round(sum(yhat_upper)), big.mark = ",")
    ),
    .groups = "drop"
  ) %>%
  arrange(desc(three_month_total))

# Format for executive presentation
formatted_summary <- forecast_summary %>%
  mutate(
    next_month_forecast = paste0(
      format(next_month, big.mark = ","),
      " (", format(next_month_lower, big.mark = ","),
      " - ", format(next_month_upper, big.mark = ","), ")"
    ),
    three_month_forecast = paste0(
      format(three_month_total, big.mark = ","),
      " (", three_month_range, ")"
    )
  ) %>%
  select(
    `Product Type` = model_name,
    `Next Month Forecast` = next_month_forecast,
    `3-Month Total Forecast` = three_month_forecast
  )

formatted_summary %>%
  kable(caption = "Executive Forecast Summary - Next 3 Months") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(1, bold = TRUE) %>%
  column_spec(2, color = "white", background = "#007bff") %>%
  column_spec(3, color = "white", background = "#28a745")
```

## Model Performance

```{r model-performance}
# Calculate comprehensive model performance metrics
performance_metrics <- model_results %>%
  filter(!is_forecast) %>%
  group_by(type, model_name) %>%
  summarise(
    observations = n(),
    rmse = sqrt(mean((month_current - yhat)^2, na.rm = TRUE)),
    mae = mean(abs(month_current - yhat), na.rm = TRUE),
    mape = mean(abs((month_current - yhat) / month_current * 100), na.rm = TRUE),
    accuracy = 100 - mape,
    r_squared = cor(month_current, yhat, use = "complete.obs")^2,
    .groups = "drop"
  ) %>%
  arrange(desc(accuracy))

# Format performance table
performance_formatted <- performance_metrics %>%
  mutate(
    RMSE = round(rmse, 2),
    MAE = round(mae, 2),
    MAPE = paste0(round(mape, 1), "%"),
    Accuracy = paste0(round(accuracy, 1), "%"),
    `R-Squared` = round(r_squared, 3),
    Grade = case_when(
      accuracy >= 95 ~ "Excellent",
      accuracy >= 90 ~ "Good",
      accuracy >= 85 ~ "Fair",
      TRUE ~ "Needs Improvement"
    )
  ) %>%
  select(
    `Product Type` = model_name,
    `Observations` = observations,
    RMSE, MAE, MAPE, Accuracy, `R-Squared`, Grade
  )

performance_formatted %>%
  kable(caption = "Model Performance Metrics") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(8, color = "white", 
              background = ifelse(performance_formatted$Grade == "Excellent", "#28a745",
                                ifelse(performance_formatted$Grade == "Good", "#17a2b8",
                                      ifelse(performance_formatted$Grade == "Fair", "#ffc107", "#dc3545"))))
```

## Demand Alerts

```{r demand-alerts}
# Generate demand alerts for significant changes
alerts <- model_results %>%
  filter(is_forecast) %>%
  group_by(type, model_name) %>%
  mutate(
    historical_avg = mean(model_results$month_current[
      model_results$type == type & !model_results$is_forecast], na.rm = TRUE),
    change_pct = ((yhat - historical_avg) / historical_avg) * 100,
    abs_change = abs(change_pct)
  ) %>%
  filter(abs_change > params$alert_threshold * 100) %>%
  arrange(desc(abs_change)) %>%
  select(
    `Product Type` = model_name,
    `Forecast Date` = ds,
    `Forecasted Usage` = yhat,
    `Historical Average` = historical_avg,
    `Change %` = change_pct
  ) %>%
  mutate(
    `Forecasted Usage` = round(`Forecasted Usage`, 0),
    `Historical Average` = round(`Historical Average`, 0),
    `Change %` = round(`Change %`, 1),
    `Alert Level` = case_when(
      abs(`Change %`) > 50 ~ "Critical",
      abs(`Change %`) > 30 ~ "High",
      TRUE ~ "Medium"
    )
  )

if (nrow(alerts) > 0) {
  alerts %>%
    kable(caption = paste("Demand Alerts (>", params$alert_threshold * 100, "% Change from Historical Average)")) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
    column_spec(6, color = "white",
                background = ifelse(alerts$`Alert Level` == "Critical", "#dc3545",
                                  ifelse(alerts$`Alert Level` == "High", "#fd7e14", "#ffc107")))
} else {
  cat("No significant demand changes detected above the", params$alert_threshold * 100, "% threshold.\n")
}
```

# Stakeholder Action Items

## Supply Chain Management

```{r supply-chain-actions}
# Generate supply chain specific recommendations
supply_chain_actions <- model_results %>%
  filter(is_forecast) %>%
  group_by(model_name) %>%
  slice(1) %>%  # Next month only
  mutate(
    procurement_urgency = case_when(
      yhat > quantile(model_results$month_current, 0.8, na.rm = TRUE) ~ "High",
      yhat > quantile(model_results$month_current, 0.6, na.rm = TRUE) ~ "Medium",
      TRUE ~ "Low"
    ),
    recommended_action = case_when(
      procurement_urgency == "High" ~ "Activate secondary suppliers, place emergency orders",
      procurement_urgency == "Medium" ~ "Increase standard order quantities",
      TRUE ~ "Maintain standard procurement schedule"
    ),
    lead_time_buffer = case_when(
      procurement_urgency == "High" ~ "2-3 weeks additional buffer",
      procurement_urgency == "Medium" ~ "1 week additional buffer", 
      TRUE ~ "Standard lead times"
    )
  ) %>%
  select(
    `Product Type` = model_name,
    `Next Month Forecast` = yhat,
    `Urgency Level` = procurement_urgency,
    `Recommended Action` = recommended_action,
    `Lead Time Buffer` = lead_time_buffer
  ) %>%
  mutate(`Next Month Forecast` = round(`Next Month Forecast`, 0)) %>%
  arrange(desc(`Next Month Forecast`))

supply_chain_actions %>%
  kable(caption = "Supply Chain Action Items - Next Month") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(3, color = "white",
              background = ifelse(supply_chain_actions$`Urgency Level` == "High", "#dc3545",
                                ifelse(supply_chain_actions$`Urgency Level` == "Medium", "#ffc107", "#28a745")))
```

## Financial Planning

```{r financial-planning}
# Financial impact analysis
financial_impact <- model_results %>%
  filter(is_forecast) %>%
  group_by(model_name) %>%
  summarise(
    three_month_forecast = sum(yhat),
    three_month_lower = sum(yhat_lower),
    three_month_upper = sum(yhat_upper),
    .groups = "drop"
  ) %>%
  mutate(
    # Assume $50 per unit cost (adjust based on actual costs)
    cost_estimate = three_month_forecast * 50,
    cost_range_lower = three_month_lower * 50,
    cost_range_upper = three_month_upper * 50,
    budget_variance = cost_estimate - mean(cost_estimate),
    cash_flow_impact = case_when(
      budget_variance > 50000 ~ "Significant increase needed",
      budget_variance > 10000 ~ "Moderate increase needed",
      budget_variance < -50000 ~ "Significant decrease expected",
      budget_variance < -10000 ~ "Moderate decrease expected",
      TRUE ~ "Within normal range"
    )
  ) %>%
  select(
    `Product Type` = model_name,
    `3-Month Forecast` = three_month_forecast,
    `Cost Estimate ($)` = cost_estimate,
    `Budget Variance ($)` = budget_variance,
    `Cash Flow Impact` = cash_flow_impact
  ) %>%
  mutate(
    `3-Month Forecast` = round(`3-Month Forecast`, 0),
    `Cost Estimate ($)` = dollar_format()(round(`Cost Estimate ($)`, 0)),
    `Budget Variance ($)` = dollar_format()(round(`Budget Variance ($)`, 0))
  )

financial_impact %>%
  kable(caption = "Financial Impact Analysis - Next Quarter") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(5, 
              color = ifelse(grepl("increase", financial_impact$`Cash Flow Impact`), "red",
                           ifelse(grepl("decrease", financial_impact$`Cash Flow Impact`), "green", "black")))
```

# Technical Appendix

## Model Parameters

```{r model-parameters}
# Display model configuration
config_table <- data.frame(
  Parameter = c("Forecast Horizon", "Confidence Level", "Alert Threshold", 
                "Yearly Seasonality", "Weekly Seasonality", "Changepoint Prior Scale"),
  Value = c(paste(params$forecast_horizon, "months"), 
            paste(params$confidence_level * 100, "%"),
            paste(params$alert_threshold * 100, "%"),
            "Enabled", "Disabled", "0.05"),
  Description = c("Number of periods to forecast ahead",
                  "Confidence interval for predictions",
                  "Threshold for generating demand alerts",
                  "Captures annual seasonal patterns",
                  "Weekly patterns disabled for monthly data",
                  "Controls trend flexibility")
)

config_table %>%
  kable(caption = "Model Configuration Parameters") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

## Data Quality Report

```{r data-quality}
# Data quality assessment
quality_report <- model_data %>%
  group_by(type) %>%
  summarise(
    total_records = n(),
    missing_values = sum(is.na(month_current)),
    date_range_start = min(ds),
    date_range_end = max(ds),
    avg_monthly_usage = round(mean(month_current, na.rm = TRUE), 1),
    data_completeness = round((1 - missing_values/total_records) * 100, 1),
    .groups = "drop"
  ) %>%
  left_join(key, by = "type") %>%
  select(
    `Product Type` = name,
    `Total Records` = total_records,
    `Missing Values` = missing_values,
    `Date Range Start` = date_range_start,
    `Date Range End` = date_range_end,
    `Avg Monthly Usage` = avg_monthly_usage,
    `Data Completeness (%)` = data_completeness
  )

quality_report %>%
  kable(caption = "Data Quality Assessment") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  column_spec(7, color = "white",
              background = ifelse(quality_report$`Data Completeness (%)` >= 95, "#28a745",
                                ifelse(quality_report$`Data Completeness (%)` >= 90, "#ffc107", "#dc3545")))
```

------------------------------------------------------------------------

## Report Information

**Report Generated:** `r Sys.Date()`\
**Forecast Period:** `r params$forecast_horizon` months ahead\
**Data Through:** `r max(model_data$ds)`\
**Next Update:** `r Sys.Date() + 30` (Monthly refresh recommended)

**Contact Information:**\
BI Team\
Email: [horizonbix.com](horizonbix@gmail.com "Horizonbix"){.email}

------------------------------------------------------------------------

*This report is automatically generated using Prophet forecasting models. For questions about methodology or data sources, please contact the Analytics Team.*
